Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-10-22 Cost_manuscript.Rmd
more intro

  Prospectus: Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it. In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015). Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort (Ainslie, 1975; Hull, 1943; Kool & Botvinick, 2018; Kool, McGuire, Rosen, & Botvinick, 2010; Treadway, Buckholtz, Schwartzman, Lambert, & Zald, 2009; Westbrook, Kester, & Braver, 2013). However, people often change their attitudes towards exerting effort in everyday decisions. For example, we might choose to take the effortful route home that we normally avoid rather than waiting for a delayed train. . Understanding the sporadic attractiveness of effort exemplified above has been elusive, and presents an important research avenue (Inzlicht, Shenhav, & Olivola, 2017). (add Loewenstein 1987 and other explanatory candidates here. I think the goal will be that there are theories speculating about when demands can be valuable for a single choice decision, or in TAFC, but point out inconclusiveness. The next paragraph should say that what's missing is comparing among costs)
  A key limitation in understanding this phenomenon is that studies often compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14]. Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16]. Furthermore, this approach fails to interrogate which type of demand people would select. Flexible preferences for effort might stem from the availability of other types of demands in the same choice environment (Kool & Botvinick, 2018).

@@

>>>>

  Prospectus: Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it. In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015). Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort (Ainslie, 1975; Hull, 1943; Kool & Botvinick, 2018; Kool, McGuire, Rosen, & Botvinick, 2010; Treadway, Buckholtz, Schwartzman, Lambert, & Zald, 2009; Westbrook, Kester, & Braver, 2013). However, people often change their attitudes towards exerting effort in everyday decisions. For example, we might choose to take the effortful route home that we normally avoid rather than waiting for a delayed train. Understanding the sporadic attractiveness of effort has been elusive, and presents an important research avenue (Inzlicht, Shenhav, & Olivola, 2017). (add Loewenstein 1987 and other explanatory candidates here. I think the goal will be that there are theories speculating about when demands can be valuable for a single choice decision, or in TAFC, but point out inconclusiveness. The next paragraph should say that what's missing is comparing among costs)
  A key limitation in understanding this phenomenon is the lack of attention given to how effort and delay might interact in the common case of choosing among demands (*An often overlooked attribute of this phenomenon is that a preference for effort is sometimes a preference over doing something else. For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting.*). Studies often compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14]. Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16]. Furthermore, this approach fails to interrogate which type of demand people would select. Flexible preferences for effort might stem from the availability of other types of demands in the same choice environment (Kool & Botvinick, 2018).

@@

studies have not focused on how effort and delay might interact in the common case of choosing among demands.
